Developing an AI-Assisted Grading System Using Large Language Models (GPT-4)

### 2024-12-18 src/paper.tex
Ordonez Edits

Recent advancements in artificial intelligence, particularly in the development of Large Language Models (LLMs), offer a promising approach to this challenge. LLMs like OpenAI's GPT-4 have demonstrated remarkable proficiency in understanding and generating human-like text by analyzing vast datasets and recognizing patterns in language. These models have the potential to transform the grading process by automating the evaluation of student responses, thereby reducing the workload on teachers.

@@

Liu et al. (2023)~\cite{Liu2023} conducted a study demonstrating GPT-4's effectiveness in grading university-level mathematics exams. The AI model was able to evaluate complex mathematical reasoning and provide grades that closely aligned with human graders. This study highlights GPT-4's potential in handling subjects that require critical thinking and problem-solving skills.

@@

For Filled-Form type assignments, the teacher needs to prompt the system by uploading a blank of the form. Figure~\ref{fig:filled-form} shows an example of what this page might look like. The teacher first identifies the location of the student identity (name and/or ID number). In the Figure, this is shown by the tan box added by the teacher around the area where a student is instructed to place their name. To add a question, the teacher clicks on the ``New Question'' link at the bottom right. The system adds a new question to the list and an associated box to go with it. Then the teach must: name the question, give the points , locate and size the associated box (shown in green) of the answer area over the blank spot they expect students to write in, and give the expected answer (not shown). Figure~\ref{fig:filled-form} shows the name area and a single question where the teacher can accomplish all these things. Here when a teacher clicks on a question in the list, they can edit the box size/location along with the name or points. The plus sign next to the red X, allows the teacher to add a sub-question. Sub-questions work the same way as questions except they appear as a sublist under the question.

@@

This process is called editing the outline and includes everything the system needs to define the assignment. The teacher can then save the outline and the system will be ready to accept student submissions. The teacher can create rubrics at this point or, more likely, defer this step grading. If the teacher decides to create the rubrics now, they progress to the webpage called ``Create Rubrics'' (see Figure~\ref{fig:page-flow}). Otherwise, they can add rubrics during grading.

A rubric defines a value subtracted from a score when applied, and a description of the reason for the deduction. The teacher can add up to 36 rubrics and they shall be numbered 0-9, and a-z. Teachers assign one or more rubrics to an answer (or group of answers when grading groups) during grading.

In the case of Free-formed typed or written assignments, the teacher gives the students questions, and the students turn in their answers as a PDF. Students may or may not include the questions, so the answer's location will vary from student to student. Here the teacher does not need to identify the location of an answer, but they do need to provide question identifiers and points for students to use when turning in the document. Figure~\ref{fig:free-form} shows an example of the teacher creating a Free-Form assignment. Notice that there is no need to draw a rectangle around the answer area and except for that task the teacher's work is identical to the filled-form assignment above.

@@

The two tasks at this stage are uploading submissions and assigning names to them. This is done in two steps. First, the assignments are uploaded by the teacher or by the individual student. Second, the teacher approves/assigns names to the assignments. This takes two screeens Manage Scans and Manage Submissions, or one screen when uploaded by the student (refer to the pages list in Figure~\ref{fig:page-flow}).

@@

In the AI assisted process, the screen shows the list of groups on the right with the main screen showing the student answers as images in a grid. Figure~\ref{fig:answer-grouping} shows an example with eight answers. The first three in the left column have been selected by clicking on the images, and at this point would form a new group if the user clicks on the ``+Create a Group'' button. The AI should group the results first, but may leave some in an ungrouped ``group.'' That is, single submissions that don't fit into a group need not be put in a separate group, but should be kept in an ``ungrouped'' group. \textit{All} groups should be listed at the right. When clicking on the group, the system should de-select any images currently selected and then show the newly selected group's images in the main page. When images are selected and the ``Create a Group'' button is clicked, the system should create the group and move the images from the current group to the new group, then display the new group and it's images.

@@

Once the system has groups created, the teach can proceed to grade the answers. The teacher does this by clicking on the Grade Answers button at the lower right in Figure~\ref{fig:answer-grouping}. Groups are graded in order that they appear on the screen with the sole exception that no matter where the ungrouped group is, it is always graded last.

@@

\begin{itemize}
    \item Pressing 0--9 or some key combination with a--z toggles the rubric as assigned or not-assigned to the group. 
    \item Left arrow takes the teacher to the previous group or individual submission.
    \item Right arrow takes the teacher to the next group or individual submission.
    \item Scrolling up or down over the rubrics scrolls through the available rubrics.
    \item Scrolling on the image zooms in and out.
    \item Clicking and dragging the image moves it around in the viewing area. 
\end{itemize}

@@

When the teacher completes all of the groups and each individual assignment in the ``ungroupped'' group, they can move on to the next question in the assignment. When they are finished with all the questions, they can publish the results so that students can see them. This ``Review Grades'' page allows the teacher to see a list of all the grades has buttons to do the following actions:

@@

\bibliographystyle{plain}
\bibliography{references}

>>>>

Recent advancements in artificial intelligence, particularly in the development of Large Language Models (LLMs), offer a promising approach to this challenge. LLMs like OpenAI's GPT-4 have demonstrated remarkable proficiency in processing and generating human-like text by analyzing vast datasets and recognizing patterns in language. These models have the potential to transform the grading process by automating the evaluation of student responses, thereby reducing the workload on teachers.

@@

Liu et al.~\cite{Liu2023} conducted a study demonstrating GPT-4's effectiveness in grading university-level mathematics exams. The AI model was able to evaluate complex mathematical reasoning and provide grades that closely aligned with human graders. This study highlights GPT-4's potential in handling subjects that require critical thinking and problem-solving skills.

@@

For Filled-Form type assignments, the teacher needs to prompt the system by uploading a blank of the form. Figure~\ref{fig:filled-form} shows an example of what this page might look like. The teacher first identifies the location of the student identity (name and/or ID number). In the Figure, this is shown by the tan box added by the teacher around the area where a student is instructed to place their name. To add a question, the teacher clicks on the ``New Question'' link at the bottom right. The system adds a new question to the list and an associated box to go with it. Then the teacher must: name the question, assign points, locate and size the associated box (shown in green) of the answer area over the blank spot they expect students to write in, and give the expected answer (not shown). Figure~\ref{fig:filled-form} shows the name area and a single question where the teacher can accomplish all these things. Here when a teacher clicks on a question in the list, they can edit the box size/location along with the name or points. The plus sign next to the red X, allows the teacher to add a sub-question. Sub-questions work the same way as questions except they appear as a sublist under the question.

@@

This process is called ``editing the outline'' and includes everything the system needs to define the assignment. The teacher can then save the outline and the system will be ready to accept student submissions. The teacher can create rubrics at this point or, more likely, defer this step until grading. If the teacher decides to create the rubrics now, they progress to the webpage called ``Create Rubrics'' (see Figure~\ref{fig:page-flow}). Otherwise, they can add rubrics during grading.

A rubric scoring guide defines text describing the error with a value subtracted from a score when applied. The teacher can add up to 36 rubrics and they shall be numbered 0-9, and a-z. Teachers assign one or more rubrics to an answer (or group of answers when grading groups) during grading.

In the case of Free-form typed or written assignments, the teacher gives the students questions, and the students turn in their answers as a PDF. Students may or may not include the questions, so the answer's location will vary from student to student. Here the teacher does not need to identify the location of an answer, but they do need to provide question identifiers and points for students to use when turning in the document. Figure~\ref{fig:free-form} shows an example of the teacher creating a Free-Form assignment. Notice that there is no need to draw a rectangle around the answer area and except for that task the teacher's work is identical to the filled-form assignment above.

@@

The two tasks at this stage are uploading submissions and assigning names to them. This is done in two steps. First, the assignments are uploaded by the teacher or by the individual student. Second, the teacher approves/assigns names to the assignments. This takes two screeens: Manage Scans and Manage Submissions, or one screen when uploaded by the student (refer to the pages list in Figure~\ref{fig:page-flow}).

@@

In the AI assisted process, the screen shows the list of groups on the right with the main screen showing the student answers as images in a grid. Figure~\ref{fig:answer-grouping} shows an example with eight answers. The first three in the left column have been selected by clicking on the images, and at this point would form a new group if the user clicks on the ``+Create a Group'' button. The AI should group the results first, but may leave some in an uncategorized group. That is, single submissions that don't fit into a group need not be put in a separate group, but should be kept in an uncategorized group. \textit{All} groups should be listed at the right. When clicking on the group, the system should de-select any images currently selected and then show the newly selected group's images in the main page. When images are selected and the ``Create a Group'' button is clicked, the system should create the group and move the images from the current group to the new group, then display the new group and its images.

@@

Once the system has groups created, the teach can proceed to grade the answers. The teacher does this by clicking on the Grade Answers button at the lower right in Figure~\ref{fig:answer-grouping}. Groups are graded in order that they appear on the screen with the sole exception that no matter where the uncategorized group is, it is always graded last.

@@

\begin{itemize}
    \item Pressing 0--9 or some key combination with a--z toggles the rubric between assigned and not-assigned to the group. 
    \item Left arrow takes the teacher to the previous group or individual submission.
    \item Right arrow takes the teacher to the next group or individual submission.
    \item Scrolling up or down over the rubrics scrolls through the available rubrics.
    \item Scrolling on the image zooms in and out.
    \item Clicking and dragging the image moves it around in the viewing area. 
\end{itemize}

@@

When the teacher completes all of the groups and each individual assignment in the uncategorized group, they can move on to the next question in the assignment. When they are finished with all the questions, they can publish the results so that students can see them. This ``Review Grades'' page allows the teacher to see a list of all the grades has buttons to do the following actions:

@@

\bibliographystyle{IEEEtran}
\bibliography{references}
